Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-07-18 arXiv-submission-v1/lqg-strings.tex
Created arXiv-submit folder. Last checks before submission.

After exploring the equations of motion ... \textbf{Luigi ... fill in summary of your work here on solving eoms and on emergent dimensions}

>>>>

After exploring the equations of motion of the area corrected string, we found that said equations can be recast as a set of Klein-Gordon equations, which for a first analysis we assumed to have constant coefficient $\mu$, however that need not be the case. The solution of these equations and their consequences for the constraints lead us to a modified \textquotedblleft Virasoro-Klein-Gordon" algebra, where the algebra modes have two indices, which in turn resulted in a truncated solution. This also had the effect of not having distinct left and right moving modes, thus there was no level-matching prohibiting spin-1 states for the closed string, which we postulated to maybe be related to the Ashtekar variables of the background geometry. The quantisation of the KG string and the Virasoro-Klein-Gordon algebra presented an anomaly-free algebra, no restrictions on the background dimensionality and no massless spin-1 or spin-2 excitations at the effective level and no negative-norm states in physical processes, with the usual $G_{\mu \nu} , B_{\mu \nu} , \Phi$ fields as part of the spin-2 spectrum.

We also briefly explored an alternative approach to incorporate LQG quantum geometric effects into string theory by considering Afshordi's ``emergent dimensions’’ model \cite{Afshordi2014Emergent} with some key insights from LQG complementing said model, creating a more concrete picture of the mechanism behind the emerging dimensions.
